Temporal Variations In Vapor Intrusion-Induced Indoor Air Contaminant Concentrations

### 2019-04-12 tex/main.tex
Wrote abstract and references new figure directory

% additional packages
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{booktabs}
\usepackage{subcaption}
\usepackage{tabularx}
\usepackage{array,multirow,graphicx}
\usepackage{comment}
\graphicspath{
  {./../figures/},
  {./../figures/2d_kde/},
  {./../figures/simulation_predictions/},
  {./../figures/pair_grids/},
  {./../figures/temporal_variability/},
}
\usepackage{lineno}
\linenumbers
% macros

@@

% title
% TODO: Change title to reflect the inclusion of preferential pathway analysis
\title{Temporal Variations In Vapor Intrusion-Induced Indoor Air Contaminant Concentrations}

% keywords
\abbreviations{VI}
\keywords{Vapor intrusion, Preferential pathways, Temporal variability, Finite element modeling, Air exchange rate}

@@

% TODO: Add abstract
\begin{abstract}

\end{abstract}

@@

\begin{figure}[htb!]
 \centering
 \caption{Mean values of the maximum change in indoor air contaminant concentration that may be expected
  over a given time period. (e.g., 1D is 1 day, 2W is 2 weeks, and 3M is 3 months). The error bars are the 95\% confidence intervals.}\label{fig:resampling}
 \includegraphics[width=\textwidth]{temporal_variability/resampling.pdf}
\end{figure}

@@

% TODO: Simplify or clarify the figure, in particular how you use the legend to highlight the max change.
\begin{figure}
 \caption{Transient simulation of a "typical" VI day, using diurnal indoor/outdoor pressure difference and air exchange rate as inputs. Effect of preferential pathway considered.}\label{fig:diurnal}
 \includegraphics[width=\textwidth]{diurnal.pdf}
\end{figure}

>>>>

% additional packages
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{booktabs}
\usepackage{subcaption}
\usepackage{tabularx}
\usepackage{array,multirow,graphicx}
\usepackage{comment}
\graphicspath{
  {./figures/},
}
\usepackage{lineno}
\linenumbers
% macros

@@

% title
\title{Temporal Variations In Vapor Intrusion-Induced Indoor Air Contaminant Concentrations}

% keywords
\abbreviations{VI}
\keywords{Vapor intrusion, Preferential pathways, Temporal variability, Finite element modeling, Air exchange rate, Indoor/outdoor pressure difference}

@@

\begin{abstract}
Temporal variability in indoor air contaminant concentrations at vapor intrusion (VI) sites has been a concern for some time.
We consider the source of the variability at VI sites located near Hill Air Force Base (AFB) in Utah, an EPA experimental house in Indiana, and Naval Air Station North Island in California and in particular how the indoor/outdoor pressure difference and air exchange rate affected indoor air contaminant concentrations at these sites.
We investigate how these dynamics differ for a site that is characterized by a preferential pathway (like Hill AFB) and a more "typical" VI site through three-dimensional fluid dynamics models and statistical analysis of the aforementioned sites.
For such a preferential pathway to impact a VI site, a medium for effective communication between the preferential pathway and the indoor air space must exist, e.g. a permeable region in the subslab (gravel layer).
Sites characterized by significant advective transport from the subslab to the indoor air space, much of short-term variability in indoor air contaminant concentration may be explained by fluctuations in indoor/outdoor pressure differences; air exchange rate drives most of the short-term variability for sites characterized by little advective transport.
\end{abstract}

@@

\begin{figure}[htb!]
 \centering
 \caption{Mean values of the maximum change in indoor air contaminant concentration that may be expected
  over a given time period. (e.g., 1D is 1 day, 2W is 2 weeks, and 3M is 3 months). The error bars are the 95\% confidence intervals.}\label{fig:resampling}
 \includegraphics[width=\textwidth]{resampling.pdf}
\end{figure}

@@

\begin{figure}
 \caption{Transient simulation of a "typical" VI day, using diurnal indoor/outdoor pressure difference and air exchange rate as inputs. Effect of preferential pathway considered.}\label{fig:diurnal}
 \includegraphics[width=\textwidth]{diurnal.pdf}
\end{figure}
